Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-13 paper/structureScene.tex
Add short discussion of MFCC + SVM results

Our results on the public part of the DCASE 2016 dataset are reported in Table \ref{table:dcase2016}, compared with a baseline using MFCCs and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. This baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes on the public part is brought from $70.8\%$ to $79.4\%$.\footnote{Challenge results on the private part of the dataset are expected to be published in August 2016.}
Furthermore, our cross-validation analysis confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.

>>>>

Our results on the public part of the DCASE 2016 dataset are reported in Table \ref{table:dcase2016}, compared with a baseline using MFCCs and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. This baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods. For comparison, we also provide the results for the same MFCC features coupled with a linear SVM classifier. Results here are slightly worse since the SVM can only discriminate between classes that are linearly separable, a limitation not present for the GMMs.
With the scattering transforms, however, the average accuracy across classes is brought from $70.8\%$ to $79.4\%$.\footnote{Challenge results on the private part of the dataset are expected to be published in August 2016.}
Furthermore, our cross-validation analysis confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.
